---
title: "Tidy Tuesday with RLadies! "
output: html_document
---

- load in libraries <br>
- read in data from github
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(dplyr)
cars <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-10-15/big_epa_cars.csv")

#View(cars)
```

- use plyr package to rename variables (make sure to detach package if you're going to use dplyr in following analyses)
```{r message=FALSE}
library(plyr)
cars <- rename(cars, c("city08" = "mpg_city"))
cars <- rename(cars, c("highway08" = "mpg_highway"))
detach(package:plyr)
```

- select variables of interest <br>
- plot a histogram of mpg_highway to get a better sense of the data <br>
- a few points around 100 so take a closer look at those...can see it's a lot of electric cars
```{r message=FALSE, warning=FALSE}
cars <- cars %>%
  select(mpg_city, mpg_highway, model, make, drive, youSaveSpend) %>%
  na.omit()

cars

ggplot(cars, aes(mpg_highway)) +
  geom_histogram()

cars %>%
  filter(mpg_highway > 75)
```

- group data by type of car (drive) and look at summary statistics of mpg_highway and youSaveSpend <br>
- building on to the histogram we looked at previously, we now divide it (facet_wrap) by drive and make it pretty!
```{r fig.height=10, fig.width = 15, fig.align='center', message=FALSE}
cars %>%
  group_by(drive) %>%
  summarise(mean_mpg_highway = mean(mpg_highway),
            mean_save = mean(youSaveSpend))

ggplot(cars, aes(mpg_highway, fill = drive)) +
  geom_histogram() +
  facet_wrap(~drive) +
  theme_bw() +
  labs(x = "Miles per Gallon on Highway") +
  theme(legend.position = "none",
        text = element_text(size = 20)) 
```

- creating a boxplot of how much people save dependent on the type of car  <br>
- note the reorder() that organises the boxplots in order of the youSaveSpend variable
```{r fig.height=10, fig.width = 15, fig.align='center'}
ggplot(cars, aes(x = reorder(drive, youSaveSpend), y = youSaveSpend, fill = drive)) +
  geom_boxplot() +
  theme_bw() +
  coord_flip() +
  labs(x = "Type of Cars", y = "Savings/Spendings") +
  theme(legend.position = "none",
        text = element_text(size = 20)) 
```

