---
title: "Tidy Tuesday - Pet Names Dataset!"
output: html_document
---

## Question of interest: What are the trends in different pets over time? 
- load in libraries <br> 
- read in data from github <br>
- we quickly found that most of the data is from 2018 and for cats and dogs <br>
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(dplyr)
library(lubridate)
library(RColorBrewer)

pets <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-03-26/seattle_pets.csv")
```

## Updated question of interest: What are the trends in cats and dogs in 2018? 
- using the lubridate(), we created separate variables for just the year and month <br>
- we filtered the data to only include 2018 and cats and dogs <br>
- then we counted the total number for each species in each month and ordered the data by month
```{r}
long_date <- mdy(pets$license_issue_date)
year <- year(long_date)
month <- month(long_date)

pets$year <- year
pets$month <- month.abb[month]
pets$month_order <- month

pet_month <- pets %>%
  filter(year == 2018) %>%
  select(license_issue_date, species, primary_breed, year, month, month_order) %>%
  filter(species == "Dog" | species == "Cat") %>%
  group_by(month, month_order, species) %>%
  count() %>%
  arrange(month_order)

pet_month
```

- creating the visualisation! <br>
- we have month on the x axis and n (number of animals) on the y axis (but note that we flipped the axes using coord_flip) <br>
- we split the data by species using facet_wrap() <br>
- we reordered the months using reorder()
- finally we changed the aesthetics to make it pretty!
```{r fig.height=10, fig.width = 15, fig.align='center'}
ggplot(pet_month, aes(x = reorder(month, -month_order), n, fill=month)) +
  geom_col() +
  facet_wrap(~species) +
  scale_fill_brewer(palette = "Set3") +
  coord_flip() +
  labs(y = "Popularity", x = "Month", title="Popularity by Species in 2018") +
  theme_minimal() +
  theme(text = element_text(size=20),
        legend.position = "none")
```

